A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-26 paper/main.tex
revise discussion

\todo{manually edit/merge slices.svg and colorbars.svg for final slicescolorbars}

@@

% Discussion
% words > no-speech
For the contrast words > no-speech, we find increased hemodynamic activity in a
bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
Our results are similar to results of studies that implemented an ISC approach
to analyze fMRI data of naturalistic auditory stimuli \citep{honey2012not,
lerner2011topographic, silbert2014coupled, wilson2008beyond}.
% dissimilarities
\todo{Which contrast captures ANY social aspects? CH: the COPEs in the
references} Contrary to previous studies \citep{ferstl2008extended,
mar2011neural}, we do not find increased medial activation in the precuneus or
medial frontal cortex. This could be attributed to the fact that the contrast
here was not designed to capture social aspects of the
narrative.\todo{wilson2007beyond: ISC medial ja, aber decreased activation
    compared to rest; current study in reverse contrast: posterior cingulate and
anterior cingulate (and insula bilaterally)}.
% (proper) nouns > con
The two contrasts contrasting nouns and proper nouns respectively to coordinate
junctions yielded increased activation that is partially located in early
sensory regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most
prominently adjacent regions bilaterally (planum temporale; superior temporal
gyrus; \citep{arsenault2015distributed, mesgarani2014phonetic}).
% interpretation 1a: large amount of semantically different nouns > narrow
% concept (conjunctions)
This could be attributed to the exploratory nature of our analysis. A high count
of heterogeneous nouns (N=\rNnAll) and proper nouns (N=\rNeAll) that were
averaged across all 300 semantic dimensions (cf. \citep{mitchell2008predicting,
huth2016natural}), and contrasted to coordinate conjunctions that offered a
comparably small amount of events (N=\rKonAll).
% interpretation 1b: not just narrow concept but also dominated by just two
% different words
Coordinate junctions were chosen because they were assumed to be temporally
uncorrelated with nouns but mostly consist of the words ``and'' (N=392) and
``but'' (N=49), and thus offered only a small amount of variance.
% interpretation 2
A second explanation might be that our phoneme regressors that assumed linear
summation of approximately \unit[70]{ms} lasting events in quick succession did
not capture a sufficiently amount of nuisance variance\todo{Reviewer 2 will ask:
    If you knew all these issues, why did you do it then? hindsight bias/HARKing
after exploratory analyses?!}.
% but...
Nevertheless and more importantly to exploratorily access the validity of the
dataset is the fact that two similar linguistic concepts (nouns and proper
nouns) embedded in a naturalistic stimulus that was not designed for linguistic
research lead to similar activation patterns\todo{That statement is only true,
if both contrasts are not (solely) driven by the conjunctions. There is no
evidence in the paper that this is not the case.}
% Within the language processing systems, early sensory regions are specialized
% for representing the immediate physical properties of the environment (form),
% while higher order regions extract increasingly abstract content (Davis and
% Johnsrude, 2003; Quiroga et al., 2005; Okada et al., 2010).

>>>>

@@

% Discussion words > no-speech
For the contrast words > no-speech, results show increased hemodynamic activity
in a bilateral cortical network including temporal, parietal and frontal regions
related to processing spoken language \citep{friederici2011brain,
hickok2007cortical,price2012twentyyears}.
% similarities to previous naturalistic speech paradigms
These clusters resemble results of previous studies that implemented an ISC
approach to analyze fMRI data of naturalistic auditory stimuli
\citep{honey2012not, lerner2011topographic, silbert2014coupled}.
% differences
We don't find significantly increased activations in midline areas (like the
posterior cingulate cortex and precuneus or anterior cingulate cortex and medial
frontal cortex) which showed correlated activity across subjects in previous
studies.
% Wilson (2008): ISC + GLM
In this regard, our results are similar to \citep{wilson2008beyond} who
implemented both an ISC and a GLM analysis. The findings by
\citep{wilson2008beyond} were that an ISC analysis yielded correlated activity
in midline areas. But the GLM analysis contrasting blocks of listening to
narratives to blocks of a resting condition yielded decreased activity in
midline areas.
\todo{fun fact regarding reverse contrast (no-speech > words):
    clusters in posterior \& anterior cingulate (and subcallosal c. \& insulae
bilaterally); could be mentioned, must be mentioned? How shortly? No figure,
pls!}

% (proper) nouns > con
The two contrasts contrasting nouns and proper nouns respectively to coordinate
junctions yielded increased activation partially located in early sensory
regions (Heschl's Gyrus; \citep{saenz2014tonotopic}) and most prominently
adjacent regions bilaterally (planum temporale; superior temporal gyrus;
\citep{arsenault2015distributed, mesgarani2014phonetic}).
% why these contrasts nous & proper nouns
We chose nouns and proper nouns for these two contrasts because they represent
linguistically similar concepts but are uncorrelated in the German language and
stimulus (cf. \ref{fig:reg-corr})
% coordinate conjunctions
We contrasted nouns and proper nouns respectively to coordinate conjunctions
because (proper) nouns and coordinate conjunctions are both linguistically
different and uncorrelated.
% “interpretation”
\todo{well what's combing up next is adventurous} Despite the fact that nouns
and proper nouns are uncorrelated, contrasts lead to spatially similar clusters
``which were not driven by a negative correlation of coordinate conjunctions
with the modeled time series (s. totally private data)''.
% why it's cool
Results suggest that our current annotation of naturalistic stimuli can be used
to create model-based analyses to test neuroscientific hypotheses.

\todo[inline]{following stuff is still here but can probably be deleted}
% interpretation 1a: large amount of semantically different nouns > narrow
% concept (conjunctions)
This could be attributed to the exploratory nature of our analysis. A high count
of heterogeneous nouns (N=\rNnAll) and proper nouns (N=\rNeAll) that were
averaged across all 300 semantic dimensions (cf. \citep{mitchell2008predicting,
huth2016natural}), and contrasted to coordinate conjunctions that offered a
comparably small amount of events (N=\rKonAll).
% interpretation 1b: not just narrow concept but also dominated by just two
% different words
Coordinate junctions were chosen because they were assumed to be temporally
uncorrelated with nouns but mostly consist of the words ``and'' (N=392) and
``but'' (N=49), and thus offered only a small amount of variance.
% interpretation 2
A second explanation might be that our phoneme regressors that assumed linear
summation of approximately \unit[70]{ms} lasting events in quick succession did
not capture a sufficiently amount of nuisance variance
